Category_Tables

### 2019-08-27 Analysis/Category_Tables.Rmd
make everything writexl

require(xlsx)
wb = createWorkbook()
sheet  = createSheet(wb, sheetName="STRING")
addDataFrame(Disease_String_Sum, sheet)
sheet  = createSheet(wb, sheetName="STRING Filtered")
addDataFrame(Disease_String_Filt_Sum, sheet)
sheet  = createSheet(wb, sheetName="Biogrid")
addDataFrame(Disease_Biogrid_Sum, sheet)

saveWorkbook(wb, "../manuscript/tables/supplementary_table_S1.xlsx")

@@

write_xlsx(msig_sum, "../manuscript/tables/supplementary_table_S2.xlsx")

>>>>

wb = list("STRING" = Disease_String_Sum %>% arrange(Category), "STRING Filtered" = Disease_String_Filt_Sum  %>% arrange(Category), "Biogrid" = Disease_Biogrid_Sum  %>% arrange(Category))

write_xlsx(wb, "../manuscript/tables/supplementary_table_S1.xlsx")

@@

write_xlsx(msig_sum,"../manuscript/tables/supplementary_table_S2.xlsx")
